Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-05-02 paper/main.tex
add table for AO COPEs

\begin{table*}
\caption{Contrasts of parameter estimates for the analysis of the audio-description.}
% das sind die zusammengefassten Kurzversionen, d.h. nicht alle Regressoren sind explizit in dem COPEs ausformuliert
\begin{tabular}{lll}
\toprule
\textbf{COPE nr.} & \textbf{description} & \textbf{aim} \\
\midrule
1 & geo, rgeo, se\_new, se\_old > non\_geo & PPA \\
2 & geo, rgeo, se\_new > non\_geo & PPA \\
3 & geo, rgeo > non\_geo & PPA <<-- THE COOL \\
4 & geo > non\_geo & PPA \\
5 & se\_new > non\_geo & PPA \\
6 & se\_new, se\_old > non\_geo & PPA \\
7 & se\_new > se\_old & PPA \\
8 & body > all\_others (excl. bpart) & EBA \\
9 & body, bpart > all\_others & EBA \\
10 & body > non\_persons (excl. bpart) & EBA \\
11 & body, bpart > non\_persons & EBA \\
12 & body, bpart > non\_persons (excl. faHead) & EBA \\
13 & fahead > all\_others & FFA \\
14 & fahead > all\_others (excl. body/parts) & FFA \\
15 & fahead > non\_persons & FFA \\
16 & fahead > non\_persons (excl. body/parts) & FFA \\
17 & obj > all\_others & LOC \\
18 & obj > all\_others (excl. fahead) & LOC \\
19 & obj > all\_others (excl. fahead, rgeo) & LOC \\
20 & obj > persons & LOC \\
21 & se\_old > se\_new & DMN \\
22 & se\_old > non\_settings & DMN \\
23 & se\_old > non\_geo & DMN \\
24 & female > male & ??? \\
25 & male > female & ??? \\
26 & persons > non\_persons (excl. body/parts) & ??? \\
27 & non\_persons (excl. body/parts) > persons & ??? \\
28 & se\_new > se\_old & visual contr. \\
29 & pe\_new > pe\_old & visual contr. \\
30 & se\_new, pe\_new > se\_old, pe\_old & visual contr. \\
31 & se\_new > pe\_old & visual contr. \\
32 & se\_new > se\_old, pe\_old & visual contr. \\
33 & se\_new, pe\_new > pe\_old & visual contr. \\
34 & se\_old > se\_new & DMN  contr. \\
35 & pe\_old > pe\_new &  DMN contr. \\
36 & no\_cut > pe\_new, pe\_old & neg. control \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}[t]
\caption{Contrasts of parameter estimates for the analysis of the audio-description.
\texttt{all non-geo} = all non-geo related regressors except furniture.}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrasted} & \textbf{aim/goal} \\
\midrule
1 & geo, groom > all non-geo & PPA \tabularnewline
2 & geo, groom, se\_new > all non-geo & PPA \tabularnewline
3 & room, se\_new, se\_old > all non-geo & PPA \tabularnewline
4 & geo > all non-geo & PPA \tabularnewline
5 & groom > all non-geo & PPA \tabularnewline
6 & se\_new > all non-geo & PPA \tabularnewline
7 & se\_new, se\_old > all non-geo & PPA \tabularnewline
8 & se\_new > se\_old & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}
